The desciption of the individual author contributions is presented by means of CRediT \footnote{Brand, A., Allen, L., Altman, M., Hlava, M. and Scott, J. (2015), Beyond authorship: attribution, contribution, collaboration, and credit. Learned Publishing, 28: 151-155. https://doi.org/10.1087/20150211}. CRediT (Contributor Roles Taxonomy) provides an accurate and detailed description of the authors' diverse contributions to the published work.% A summarised description of the CRediT categories is provided in Table~\textit{CRediT}.

%-----------------------------------------------
\paperitem % Uncertainty analysis
	\textbf{RC:} Methodology, Software, Validation, Formal analysis, Investigation, Data Curation, Writing - Original Draft, Writing - Review \& Editing, Visualization;
	\textbf{AG:} Methodology, Software, Formal analysis, Investigation, Writing - Original Draft, Writing - Review \& Editing, Visualization;
	\textbf{CSV:} Conceptualization, Methodology, Software, Writing - Original Draft, Writing - Review \& Editing, Supervision;
	\textbf{SD:} Conceptualization, Methodology, Software, Resources, Writing - Original Draft, Writing - Review \& Editing, Supervision, Project administration, Funding acquisition.

%-----------------------------------------------
\paperitem % Plasmas
	\textbf{RC:} Conceptualization, Methodology, Software, Validation, Formal analysis, Investigation, Data Curation, Writing - Original Draft, Writing - Review \& Editing, Visualization;
	\textbf{TM:} Conceptualization, Methodology, Software, Validation, Formal analysis, Investigation, Data Curation, Writing - Original Draft, Writing - Review \& Editing, Visualization;
	\textbf{SD:} Conceptualization, Methodology, Writing - Review \& Editing, Supervision, Project administration, Funding acquisition;
	\textbf{AI:} Conceptualization, Methodology, Writing - Review \& Editing, Supervision, Project administration, Funding acquisition;
	\textbf{MK:} Conceptualization, Methodology, Software, Resources, Writing - Review \& Editing, Visualization, Supervision, Project administration, Funding acquisition;

%-----------------------------------------------
\paperitem % Slot jet in crossflow
	\textbf{RC:} Methodology, Software, Validation, Formal analysis, Investigation, Data Curation, Writing - Original Draft, Writing - Review \& Editing, Visualization, Project administration;
	\textbf{GS:} Software, Validation, Investigation, Writing - Original Draft, Writing - Review \& Editing, Visualization;
	\textbf{MR:} Methodology, Validation, Investigation, Writing - Review \& Editing, Supervision;
	\textbf{AI:} Conceptualization, Methodology, Investigation, Resources, Writing - Review \& Editing, Supervision, Project administration, Funding acquisition;
	\textbf{SD:} Conceptualization, Methodology, Validation, Resources, Writing - Review \& Editing, Supervision, Project administration, Funding acquisition.

%-----------------------------------------------
\paperitem % LGPC vs RL
	\textbf{RC:} Conceptualization, Methodology, Software, Validation, Formal analysis, Investigation, Data Curation, Writing - Original Draft, Writing - Review \& Editing, Visualization, Project administration;
	\textbf{GCM:} Software, Formal analysis, Writing - Original Draft, Writing - Review \& Editing, Visualization;
	\textbf{IF:} Methodology, Software, Writing - Original Draft, Writing - Review \& Editing, Visualization;
	\textbf{BN:} Conceptualization, Resources, Writing - Review \& Editing, Supervision, Funding acquisition;
	\textbf{AI:} Conceptualization, Resources, Writing - Review \& Editing, Supervision, Project administration, Funding acquisition;
	\textbf{SD:} Conceptualization, Resources, Writing - Original Draft, Writing - Review \& Editing, Supervision, Project administration, Funding acquisition;
		
\paperitem % LGAC in TBL for HTE
	\textbf{RC:} Conceptualization, Methodology, Software, Validation, Formal analysis, Investigation, Data Curation, Writing - Original Draft, Writing - Review \& Editing,
Visualization, Project administration ;
	\textbf{AI:} Conceptualization, Methodology, Resources, Writing - Review \&
Editing, Supervision, Project administration, Funding acquisition;
	\textbf{SD:} Conceptualization, Methodology, Software, Validation, Investigation, Resources, Writing - Review \& Editing, Supervision, Project administration, Funding acquisition.\\%

\vspace{1cm}
\noindent Acronyms correspond to:
\begin{itemize}
    \item[RC] Rodrigo \textbf{Castellanos}. Universidad Carlos III de Madrid. \small{\textit{PhD Candidate}}.
    \item[SD] Stefano \textbf{Discetti}. Universidad Carlos III de Madrid. \small{\textit{Advisor and Tutor}}. 
    \item[AI] Andrea \textbf{Ianiro}. Universidad Carlos III de Madrid. \small{\textit{Advisor}}.
    \item[MR] Marco \textbf{Raiola}. Universidad Carlos III de Madrid.
    \item[CSV] Carlos \textbf{Sanmiguel-Vila}. Universidad Carlos III de Madrid.
    \item[AG] Alejandro \textbf{G\"uemes}. Universidad Carlos III de Madrid.
    \item[GS] Gianfranco \textbf{Salih}. Universidad Carlos III de Madrid.
    \item[IF] Ignacio \textbf{de la Fuente}. Universidad Carlos III de Madrid.
    \item[MK] Marios \textbf{Kotsonis}. Technische Universiteit Delft.
    \item[TM] Theodoros \textbf{Michelis}. Technische Universiteit Delft.
    \item[BN] Bernd R. \textbf{Noack}. Harbin Institute of Technology.
    \item[GCM] Guy Y. \textbf{Cornejo Maceda}. Harbin Institute of Technology.
\end{itemize}


%\begin{table}
%\centering
%\begin{tabular}{>{\raggedright\arraybackslash}p{0.25\linewidth-2\tabcolsep}
%>{\raggedright\arraybackslash}p{0.75\linewidth-2\tabcolsep}}
%\toprule
%\tiny{Term} & \tiny{Definition } \\
%\midrule
%\tiny{Conceptualization} & \tiny{Ideas; formulation or evolution of overarching research goals and aims } \\
%\tiny{Methodology} & \tiny{Development or design of methodology; creation of models} \\
%\tiny{Software} & \tiny{Programming, software development; designing computer programs; implementation of the computer code and supporting algorithms; testing of existing code components} \\
%\tiny{Validation} & \tiny{Verification, whether as a part of the activity or separate, of the overall replication/ reproducibility of results/experiments and other research outputs} \\
%\tiny{Formal analysis} & \tiny{Application of statistical, mathematical, computational, or other formal techniques to analyze or synthesize study data} \\
%\tiny{Investigation} & \tiny{Conducting a research and investigation process, specifically performing the experiments, or data/evidence collection} \\
%\tiny{Resources} & \tiny{Provision of study materials, reagents, materials, patients, laboratory samples, animals, instrumentation, computing resources, or other analysis tools} \\
%\tiny{Data Curation} & \tiny{Management activities to annotate (produce metadata), scrub data and maintain research data (including software code, where it is necessary for interpreting the data itself) for initial use and later reuse} \\
%\tiny{Writing - Original Draft} & \tiny{Preparation, creation and/or presentation of the published work, specifically writing the initial draft (including substantive translation)} \\
%\tiny{Writing - Review \& Editing} & \tiny{Preparation, creation and/or presentation of the published work by those from the original research group, specifically critical review, commentary or revision – including pre-or postpublication stages} \\
%\tiny{Visualization} & \tiny{Preparation, creation and/or presentation of the published work, specifically visualization/ data presentation} \\
%\tiny{Supervision} & \tiny{Oversight and leadership responsibility for the research activity planning and execution, including mentorship external to the core team} \\
%\tiny{Project administration} & \tiny{Management and coordination responsibility for the research activity planning and execution} \\
%\tiny{Funding acquisition} & \tiny{Acquisition of the financial support for the project leading to this publication} \\
%\bottomrule
%\end{tabular}
%\caption*{CRediT: Description of CRediT categories based on Brand et al. (2015), Learned Publishing 28(2).}
%\end{table}